---
title: "Process ddPCR data"
author: "Adelaide Roguet"
date: "3/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages, include=FALSE}
rm(list=ls(all=FALSE))# But the best is to uncheck all the boxes "R Session" and "Workspace" in the preferences of RStudio and RESTART RStudio all the time you run this script!
library(twoddpcr) #install: https://www.bioconductor.org/packages/release/bioc/html/twoddpcr.html
library(ggplot2)
library(data.table)
library(dplyr)
library(stringr)
library(ezknitr)
```


# Preparation
### Set the working directory
OneDrive desktop has to be install on your computer. \
Once install, you will have to synchronize the SARS-CoV-2 folder to your files, to do that, you just have to create a shortcut of the SARS-CoV-2 folder. On your favorite browser, just right click on SARS-CoV-2 folder and click on "Add shortcut".  \
You are good to go :-)
```{r}
working_directory="~/OneDrive - UWM/SARS-CoV-2/DATA/ddPCR data/"
```

### Set the run-ID
The run-ID is the name of the directory containing the amplification/cluster .csv files
It is important that folder start with: 
YEAR-MONTH-DAY space TARGET, such as 2021-1-24 for a N1N2 run performed on January 24, 2021
```{r}
run_ID = "2-25 PMMOV copy"
```

### Set the sample info
.csv name (in the folder)
```{r}
samples.info = "2-25 PMMoV.csv" 
```



# Process the ddPCR data 

### Import the functions
```{r echo=FALSE, error=FALSE, message=FALSE}
knitr::opts_knit$set(root.dir = paste0(working_directory, run_ID, "/"))
file.copy("~/OneDrive - UWM/SARS-CoV-2/DATA/ddPCR data/function_ddPCR_v4.R", ".", overwrite = TRUE)
source("function_ddPCR_v4.R")
```


## Run analysis
```{r dplyr, stringr, data.table}
Analyse_ddPCR_results()
```



